Improving \textsl{Gaia} parallax precision \\ with a data-driven model of stars

### 2017-06-06 paper/paper.tex
selection function stuff again

@@

  Beyond this, the choice of the Gaussian form itself for the mixture is
  questionable. The Gaussian has great properties, that we capitalize on
  both at the prior-generation stage (with \xd), and at the photometric-parallax
  stage (capitalizing on Gaussian product rules). We could move to other
  forms, but they would be extremely expensive, computationally.
\item[no physics] Although it is presented as an advantage of our
  method that we never make any use of physical models, it is also
  brings some significant disadvantages: For example, the \cmd\ contains
  features that are obvious products of stellar evolution, but doesn't in
  itself inform the theory or models of stellar evolution, because our
  mixture-of-Gaussian \cmd\ model is divorced from any theoretical ideas
  about stars. For another, stellar evolution models are in fact very
  predictive and successful; our model does not capitalize in any way on
  those successes. A next-generation model might be designed to be data-driven
  but nonetheless capitalize on physics-driven successes. One framework
  for that would be to fit not the \cmd\ but rather deviations of the \cmd\ away
  from a good physics-based model prediction.
\end{description}

>>>>

  Those inhomogeneities are unlikely to affect the \cmd results; we effectively model the average distribution of the \tgas--\tmass\ intersection. 
  By modeling the selection function in detail, one could improve the quality of the inferred \cmb, its effect on individual objects, and its connection to physical models of the Milky Way. 

@@

  Beyond this, the choice of the Gaussian form itself for the mixture is
  questionable. The Gaussian has great properties, that we capitalize on
  both at the prior-generation stage (with \xd), and at the photometric-parallax
  stage (capitalizing on Gaussian product rules). We could move to other
  forms, but they would be extremely expensive, computationally.
\item[no physics] Although it is presented as an advantage of our
  method that we never make any use of physical models, it is also
  brings some significant disadvantages: For example, the \cmd\ contains
  features that are obvious products of stellar evolution, but doesn't in
  itself inform the theory or models of stellar evolution, because our
  mixture-of-Gaussian \cmd\ model is divorced from any theoretical ideas
  about stars. For another, stellar evolution models are in fact very
  predictive and successful; our model does not capitalize in any way on
  those successes. A next-generation model might be designed to be data-driven
  but nonetheless capitalize on physics-driven successes. One framework
  for that would be to fit not the \cmd\ but rather deviations of the \cmd\ away
  from a good physics-based model prediction. This would also require modeling the selection function of the data under consideration.
\end{description}
